The title

### 2020-11-23 scripts/draft_play.Rmd
Xiaoyu Liu_peer review

 ggplot(BCdatastripped_spedcat, aes(x = SCHOOL_YEAR, y = NUMBER_OF_STUDENTS)) +
  geom_line(color = "cornflowerblue") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   facet_wrap(~SPECIAL_NEEDS_CODE) +
   labs(title = "BC Provincial Headcount of Students with Exceptionalities by Category",
        x = "School Year",
        y = "Headcount")

@@

@@

cleanest_primo <- cleanest_primo %>% 
  select(-six_to_twentyone_total, -x24)

@@

@@

>>>>

 ggplot(BCdatastripped_spedcat, aes(x = SCHOOL_YEAR, y = NUMBER_OF_STUDENTS)) +
  geom_line(color = "cornflowerblue") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   facet_wrap(~SPECIAL_NEEDS_CODE) +
   labs(title = "BC Provincial Headcount of Students with Exceptionalities by Category",
        x = "School Year",
        y = "Headcount")
#strength 1: I really like the data visualization. It is very clear! 
```

@@

# strength 2: I really like the data cleaning part. They used pivot_longer to make the data more clear! 
```

@@

# Strength 3: Remove_empty: this function is great to remove NAs.
cleanest_primo <- cleanest_primo %>% 
  select(-six_to_twentyone_total, -x24)

@@

# This is the part the I learned. I learned the parse_number function to .This drops any non-numeric characters before or after the first number. The grouping mark specified by the locale is ignored inside the number.
```

@@

#improvement: I am not sure what does the second ```r``` includes. maybe you could delete. 
```
